J-ReCoVer: Java Reducer Commutativity Verifier

### 2018-11-11 draft.tex
polish sections 1-4
conclusion

\begin{figure}
	\begin{minipage}{0.32\textwidth}
		\begin{algorithm}[H]
			$m := \cur$; \;
			\Loop{}{
				\uIf{ $\cur > m$}{
					$m := \cur$ 
				}
			};
			$out(m)$\;
		\end{algorithm}
		\caption*{(a) max}
	\end{minipage}	
	\hspace{-0.5cm}
	\begin{minipage}{0.3\textwidth}
		\begin{algorithm}[H]
			$s := 0;c:=0$; \;
			\Loop{}{
				$s := s+\cur$;\;
				$c := c+1$ 
			};
			$o := s/c$;\;
			$out(o)$\;
		\end{algorithm}
		\caption*{(b) average}
	\end{minipage}	
	\begin{minipage}{0.4\textwidth}
		\begin{algorithm}[H]
			$a:=*;s := 0; c:=0$;\;
			\Loop{}{
				$s := s+(\cur-a)^2$; \;
				$c := c+1$ 
			};
			$o := s/c$;\;
			$out(o)$
		\end{algorithm}
		\caption*{(c) standard derivation}
	\end{minipage}	
	\caption{Example of reducer programs}
	\label{fig:reducer_example}
\end{figure}

@@

\subsection{Limitations and assumptions}
At the back-end, we use SMT theory of integer arithmetics as the reasoning tool. In this implementation, we do not handle more advanced data-types such as string and floating point. 
The problem of variable overflow is not handled by this tool. In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow. Even the basic example that computes the sum of all input values, overflow can occur when a list contains two maximal 64-bit integer values is used as the input. Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze. We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur. The programmer can than check if their data set fits the computed bound and use lager data type in the program when needed. So overflow will not occurs in the data set of interests.

@@

\begin{table}[htb]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		& &W/O optimization	& With optimization\\
		\hline
		\hline
		\multirow{4}{*}{Open repositories}&Commutative& 8&106\\ 
		\cline{2-4}
		&Non-commutative&9&9\\
		\cline{2-4}
		&Unknown&101&3\\
		\cline{2-4}
		&Precision& 14.4\% & 97.5\%\\
		\hline
		\hline
		\multirow{4}{*}{Literatures}&Commutative& 0&9\\
		\cline{2-4}
		&Non-commutative&1&1\\
		\cline{2-4}
		&Unknown&9&0\\
		\cline{2-4}
		&Precision& 10\% & 100\%\\
		\hline
	\end{tabular}
	\caption{The improvement of precision using data flow analysis. The row ``Precision'' is calculated as the number of examples that J-Recover returns commutative or non-commutative divided by the total number of example.}
	\label{tab:opt1}
\end{table}

@@

	\begin{minipage}{0.6\textwidth}
\begin{tabular}{|l|l|l|l|l|l|l|}
	\hline
	& \multicolumn{3}{c|}{\small W/O optimization}	& \multicolumn{3}{c|}{\small With optimization} \\
	\hline
	\small Lines & \small Average & \small Median & \small T/O & \small Average & \small Median & \small T/O \\
	\hline
	\hline
	50	&	11.104	&	10.446	&	0	&	10.284	&	10.193	&	0	\\
	\hline                                                                              
	100	&	19.766	&	11.239	&	1	&	29.544	&	11.172	&	3	\\
	\hline                                                                             
	150	&	88.741	&	17.943	&	12	&	63.931	&	13.984	&	7	\\
	\hline                                                                             
	200	&	88.741	&	169.456	&	26	&	63.931	&	13.984	&	7	\\
	\hline                                                                             
	250	&	232.348	&	300.000	&	43	&	175.976	&	248.998	&	30	\\
	\hline
\end{tabular}
	\end{minipage}	
	\begin{minipage}{0.4\textwidth}
\scalebox{0.6}{
	\begin{tikzpicture}
	\begin{axis}[%
	xmin=-5, xmax=320,
	ymin=-5, ymax=320,
	xlabel={\Large with optimization},
	ylabel={\Large w/o optimization}
	]
	\addplot[scatter,only marks,%
	scatter src=explicit symbolic, mark=x]%
	file {plot_data/optimize.data};
	\draw (-100,-100) -- (400, 400);
	\end{axis}
	\end{tikzpicture}
}		
	\end{minipage}

@@

% Optimization compare graph
Bounded model checking (BMC) is another approach to create the $F$ function in Equations~\ref{eq:commu} and \ref{eq:commu2}. Although we use symbolic execution in J-Recover, it is interesting to see how good BMC works in checking the commutativity of reducer examples. In this evaluation, we use the same random reducer program generator. One major different difference is that for the BMC part, we directly generate the corresponding $F$ formula in the BMC-style without going through the Soot framework. So the number of variables in the formula is much less than the symbolic execution version. The results can be found in Table~\ref{tab:bmc}. For symbolic execution, we first use J-Recover to generate the formula for evaluation. For BMC, the formula is directly generated by the random generator. In this evaluation, we see that the performance of using BMC is in general better, less timeout and lower average execution time, so we plan to also include a BMC engine in the next version. However, from the scatter plot we can see there are multiple cases that  can be solved using symbolic execution but are slower or even failed using BMC. So the best strategy should be keep the both engine and switch to another if one fails.

@@

\begin{minipage}{0.7\textwidth}	
	\begin{tabular}{|l||l|l| l||l|l|}
\hline
		Java& \multicolumn{2}{c|}{\small BMC}	& Jimple& \multicolumn{2}{c|}{\small Symbolic Exec.} \\
\hline
		\small Lines/Vars & \small Average & \small  \small T/O & Lines/Vars& \small Average & \small  \small T/O \\
\hline
\hline
		50/5	&	0.063		&	0	&	72.85/65.7	&	0.139	&		0	\\
\hline
		100/10	&	0.840	&		0	&	129.95/120.85	&	3.052	&	0	\\
\hline
		150/15	&	28.459	&		1	&	186.9/175.6	&	36.233	&		1	\\
\hline
		200/20	&	76.220	&		2	&	243.75/230.6	&	89.730	&		5	\\
\hline
		250/25	&	84.358	&		5	&	300.55/285.85	&	172.482	&		10	\\
\hline
	\end{tabular}
		\end{minipage}		
	\begin{minipage}{0.29\textwidth}
\scalebox{0.5}{
\begin{tikzpicture}
\begin{axis}[%
xmin=-5, xmax=320,
ymin=-5, ymax=320,
xlabel=J-ReCoVer(s),
ylabel=BMC(s)
]
\addplot[scatter,only marks,%
scatter src=explicit symbolic, mark=x]%
file {plot_data/bmc.data};
\draw (-100,-100) -- (400, 400);
\end{axis}
\end{tikzpicture}
}			
		\end{minipage}		
	\caption{The performance of using BMC and symbolic execution. Each table cell is the result obtained from 20 randomly generated cases.}
	\label{tab:bmc}

\end{table}

\section{Concluding Remarks}

\bibliographystyle{splncs-sorted}
\bibliography{refs}

>>>>

\begin{figure}
	\begin{minipage}{0.32\textwidth}
		\begin{algorithm}[H]
			$m := \cur$; \;
			\Loop{}{
				$t:=\cur$;\;
				\uIf{ $t > m$}{
					$m := t$ 
				}
			};
			$out(m)$\;
		\end{algorithm}
		\caption*{(a) max}
	\end{minipage}	
	\hspace{-0.5cm}
	\begin{minipage}{0.3\textwidth}
		\begin{algorithm}[H]
			$s := 0;c:=0$; \;
			\Loop{}{
				$s := s+\cur$;\;
				$c := c+1$ 
			};
			$o := s/c$;\;
			$out(o)$\;
		\end{algorithm}
		\caption*{(b) average}
	\end{minipage}	
	\begin{minipage}{0.4\textwidth}
		\begin{algorithm}[H]
			$a:=*;s := 0; c:=0$;\;
			\Loop{}{
				$s := s+(\cur-a)^2$; \;
				$c := c+1$ 
			};
			$o := s/c$;\;
			$out(o)$
		\end{algorithm}
		\caption*{(c) standard derivation}
	\end{minipage}	
	\caption{Example of reducer programs}
	\label{fig:reducer_example}
\end{figure}

@@

@@

\begin{table}[htb]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		& &W/O optimization	& With optimization\\
		\hline
		\hline
		\multirow{4}{*}{Open repositories}&Commutative& 0&106\\ 
		\cline{2-4}
		&Non-commutative&8&9\\
		\cline{2-4}
		&Unknown&110&3\\
		\cline{2-4}
		&Precision& 6.8\% & 97.5\%\\
		\hline
		\hline
		\multirow{4}{*}{Literatures}&Commutative& 0&9\\
		\cline{2-4}
		&Non-commutative&1&1\\
		\cline{2-4}
		&Unknown&9&0\\
		\cline{2-4}
		&Precision& 10\% & 100\%\\
		\hline
	\end{tabular}
	\caption{The improvement of precision using data flow analysis. The row ``Precision'' is calculated as the number of examples that J-Recover returns commutative or non-commutative divided by the total number of example.}
	\label{tab:opt1}
\end{table}

@@

	\begin{minipage}{0.6\textwidth}
\begin{tabular}{|l|l|l|l|l|l|l|}
	\hline
	& \multicolumn{3}{c|}{\small W/O optimization}	& \multicolumn{3}{c|}{\small With optimization} \\
	\hline
	\small Lines & \small Average & \small Median & \small T/O & \small Average & \small Median & \small T/O \\
	\hline
	\hline
	50	&	4.3	    &   3.7	&	0	&	4.7	&	3.6	&	0	\\
	\hline                                                                      
	100	&	35.8	&	5.1&	4	&	37.2	&	4.5	&	6	\\
	\hline                                                                     
	150	&	92.3	&	12.3&	13	&	74.0	&	7.5	&	9	\\
	\hline                                                                     
	200	&	156.6	&	179.7&	25	&	138.1	&	48.2	&	25	\\
	\hline                                                                     
	250	&	196.8	&	300.0&	35	&	175.9	&	274.9	&	30	\\
	\hline
\end{tabular}
	\end{minipage}	
	\begin{minipage}{0.4\textwidth}
\scalebox{0.6}{
	\begin{tikzpicture}
	\begin{axis}[%
	xmin=-5, xmax=320,
	ymin=-5, ymax=320,
	xlabel={\Large with optimization},
	ylabel={\Large w/o optimization}
	]
	\addplot[scatter,only marks,%
	scatter src=explicit symbolic, mark=x]%
	file {plot_data/optimize.data};
	\draw (-100,-100) -- (400, 400);
	\end{axis}
	\end{tikzpicture}
}		
	\end{minipage}

@@

\hide{
% Optimization compare graph
Bounded model checking (BMC) is another approach to create the $F$ function in Equations~\ref{eq:commu} and \ref{eq:commu2}. Although we use symbolic execution in J-Recover, it is interesting to see how good BMC works in checking the commutativity of reducer examples. In this evaluation, we use the same random reducer program generator. One major different difference is that for the BMC part, we directly generate the corresponding $F$ formula in the BMC-style without going through the Soot framework. So the number of variables in the formula is much less than the symbolic execution version. The results can be found in Table~\ref{tab:bmc}. For symbolic execution, we first use J-Recover to generate the formula for evaluation. For BMC, the formula is directly generated by the random generator. In this evaluation, we see that the performance of using BMC is in general better, less timeout and lower average execution time, so we plan to also include a BMC engine in the next version. However, from the scatter plot we can see there are multiple cases that  can be solved using symbolic execution but are slower or even failed using BMC. So the best strategy should be keep the both engine and switch to another if one fails.

@@

\begin{minipage}{0.7\textwidth}	
	\begin{tabular}{|l||l|l| l||l|l|}
\hline
		Java& \multicolumn{2}{c|}{\small BMC}	& Jimple& \multicolumn{2}{c|}{\small Symbolic Exec.} \\
\hline
		\small Lines/Vars & \small Average & \small  \small T/O & Lines/Vars& \small Average & \small  \small T/O \\
\hline
\hline
		50/5	&	0.1		&	0	&	72.9/65.7	&	0.1	&		0	\\
\hline
		100/10	&	0.8	&		0	&	130.0/120.9	&	3.1	&	0	\\
\hline
		150/15	&	28.5	&		1	&	186.9/175.6	&	36.2	&		1	\\
\hline
		200/20	&	76.2	&		2	&	243.8/230.6	&	89.7	&		5	\\
\hline
		250/25	&	84.4	&		5	&	300.6/285.9	&	172.5	&		10	\\
\hline
	\end{tabular}
		\end{minipage}		
	\begin{minipage}{0.29\textwidth}
\scalebox{0.5}{
\begin{tikzpicture}
\begin{axis}[%
xmin=-5, xmax=320,
ymin=-5, ymax=320,
xlabel=Symbolic Exec.(s),
ylabel=BMC(s)
]
\addplot[scatter,only marks,%
scatter src=explicit symbolic, mark=x]%
file {plot_data/bmc.data};
\draw (-100,-100) -- (400, 400);
\end{axis}
\end{tikzpicture}
}			
		\end{minipage}		
	\caption{The performance of using BMC and symbolic execution. Each table cell is the result obtained from 20 randomly generated cases.}
	\label{tab:bmc}

\end{table}
}
\section{Concluding Remarks}
We believe that simpler but more restricted language/framework will be the trend for parallel program development. It lowers the barrier for writing parallel program. So experts in other domains such as data science and machine learning can use the power of parallel data processing with much less efforts. Many of their applications do not need the full power of message passing programming so they do not need to those build their programs on top of traditional means such as MPI or socket programming. MapReduce framework is a pioneer in this kind of frameworks for data parallel computation. Its successors such as Spark, Flink, Beam, and Google Cloud Dataflow, still share many features of its design. We believe the design of J-Recover will lead to significant impact to the verification/testing of programs under such frameworks.

The current version of J-Recover shares similar limitation with SMT-based software verification tools.
We use SMT theory of integer and real number arithmetics as the reasoning tool. In this implementation. We do not handle more advanced data-types such as string and floating point. The problem of variable overflow is not handled by this tool. In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow. Even the basic example that computes the sum of all input values, overflow can occur when a list contains two maximal 64-bit integer values is used as the input. Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze. We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur. The programmer can than check if their data set fits the computed bound and use lager data type in the program when needed. So overflow will not occurs in the data set of interests.

%\bibliographystyle{splncs-sorted}
\bibliography{refs}
